Augmenting the DonorsChoose.org Corpus for Meta-Learning \thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Drop page-count
Furthermore, comment out some unenforced `\setlength` command.
paper/main.tex: Readd supervisors and BeelGroup

	\makeatletter
	% Insert a float barrier before subsections just like the package 'placeins' does for sections
	%\AtBeginDocument{%
	%	\expandafter\renewcommand\expandafter\subsection\expandafter{%
	%		\expandafter\@fb@secFB\subsection
	%	}%
	%}
	\makeatother
	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
	\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text

@@

@@

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{G.Edenhofer@campus.lmu.de, collinsa@tcd.ie}
}

@@

\begin{abstract}
The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items. The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations. Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested. This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches. In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus. It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment. The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set. The augmented dataset and the source code are released into the public domain at \href{https://github.com/Edenhofer/Augmented-DonorsChoose.org-Dataset}{GitHub:Edenhofer/Augmented-DonorsChoose.org-Dataset}.

>>>>

	\makeatletter
	% Insert a float barrier before subsections just like the package 'placeins' does for sections
	%\AtBeginDocument{%
	%	\expandafter\renewcommand\expandafter\subsection\expandafter{%
	%		\expandafter\@fb@secFB\subsection
	%	}%
	%}
	\makeatother
	\setlength{\intextsep}{1em}  % Reduce excessive spacing between float and text
	%\setlength{\textfloatsep}{1em}  % Reduce excessive spacing between caption and text

@@

	\pagenumbering{gobble}  % Disable page-numbering

@@

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
}

@@

\begin{abstract}
The DonorsChoose.org dataset of past donations provides a big and feature-rich corpus of users and items. The dataset matches donors to projects in which they might be interested in and hence is intrinsically about recommendations. Due to the availability of detailed item-, user- and transaction-features, this corpus represents a suitable candidate for meta-learning approaches to be tested. This study aims at providing an augmented corpus for further recommender systems studies to test and evaluate meta-learning approaches. In the augmentation, metadata of collaborative and content-based filtering techniques is amended to the corpus. It is further extended with aggregated statistics for users and transactions and an exemplary meta-learning experiment. The performance in the learning subsystem is measured via the recall of recommended items in a Top-N test set. The augmented dataset and the source code are released into the public domain at \href{https://github.com/BeelGroup/Augmented-DonorsChoose.org-Dataset}{GitHub:BeelGroup/Augmented-DonorsChoose.org-Dataset}.
